Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/miccai2012.tex
miccai 2012: shell model and method sections
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@339 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
comments about the intro
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@344 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
modifs in section 2
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@348 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
modifs on section 3
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@351 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
Shortened and improved introduction. Improved (not yet final) paper title.
git

\usepackage{color}
\usepackage{amsmath}
\usepackage[tight]{subfigure}
\usepackage{listings}
\definecolor{darkgray}{rgb}{0.2,0.2,0.2}

@@

\title{Towards planning of infantile cardiac surgery based on simulation}

\author{PaperID:} % TODO

@@

\section{Blood Vessel Model}
\input{shell-model.tex}

\section{Simulation of Surgical Procedures}
\input{simulation.tex}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage[tight]{subfigure}
\usepackage{listings}
\definecolor{darkgray}{rgb}{0.2,0.2,0.2}
\usepackage{ulem}

@@

\title{Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements}

\author{Stefan Kislinskiy\inst{1}
\and Tom\'{a}\v{s} Golembiovsk\v{y}\inst{2,3}
\and Christian Duriez\inst{2}
\and Eug\'{e}nie Riesenkampff\inst{4}
\and Titus Kuehne\inst{4}
\and H.-P. Meinzer\inst{1}
\and Tobias Heimann\inst{1}}

\institute{German Cancer Research Center (DKFZ), Heidelberg, Germany
\and Inria, Lille, France
\and Faculty of Informatics, Masaryk University, Brno, Czech Republic
\and German Heart Institute Berlin (DHZB), Berlin, Germany}

@@

\section{Blood Vessel Model based on shell theory}
\input{shell-model.tex}

\section{Simulation of Surgical Procedures}
\label{sec-method}
\input{simulation.tex}

### 2012-03-01 Doc/Miccai/results.tex
Added authors and institutes. Began results section. Began conclusion section.
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@357 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

Example with 3 diff. surgical procedures

Parameters

Limitations (getting image data, meshes, dynamic remeshing, same number of nodes)

>>>>

In order to show an improvement on existing predictive simulation systems for CHD corrective surgeries, we want to demonstrate that our blood vessel model based on thin shell elements is
\begin{enumerate}
\item physically accurate,
\item converges to expected results with a low amount of elements,
\item is able to simulate low-level surgical procedures universally.
\end{enumerate}
A quantitative validation by means of a comparision to real pre- and post-surgery image data is impossible at present. This is mainly due to ethical issues that arise during image data acquirement of infants, i.e. necessary heart rate lowering medications or exposure to radiation. There is no such data available that is obtained shortly after surgeries in infants where the growth of the patient would not interfere comparison. However, qualitative comparisons to a real image data set acquired months after a surgical intervention and to an elastic tube manipulated by hand, which confirm a principal suitability of predictive simulations for surgery planning, can be found in \cite{Li2009}.

We close this section with a discussion about the limitations and constraints of our approach which have great impact on the mesh generation prior to simulation.

\subsection{Accuracy}

Figure \ref{fig-deformations} shows bending and twisting of an elastic tube manipulated by hand compared to the simulation results of \cite{Li2009} and our method. These kinds of blood vessel deformations are likely to occur during surgery. Our results are close to the real deformations as expected due to the physically based formulation of thin shell elements.

\subsection{Convergence}

It is important to minimize the number of shell elements to reduce computation time. This is the key factor to enable an interactive simulation system that is accepted by surgeons to simulate multiple surgical approaches in succession. The bending of thin shell elements allows to reduce their number by still representing the tubular structure of blood vessels while maintaining their physical behavior appropriately. Figure \ref{fig-convergence} shows simulation results of a strongly deformed tube represented by different numbers of thin shell elements. With only eight vertices along the circumference of the tube the simulation result is comparable to a simulation result with high element count. We map a fine polygonal mesh to the coarse shell element meshes to visualize their bending detail and therefore get comparable results that correlates with the true shape of the simulated tube.

\subsection{Low-level surgical procedures}

TODO: Use the remaining space we have in the paper. We should consider to shorten other sections.

\subsection{Limitations and Constraints}

%Example with 3 diff. surgical procedures
%Parameters
%Limitations (getting image data, meshes, dynamic remeshing, same number of nodes)
